Reducing RES Droughts through the integration of wind and PV

### 2025-01-15 Article2/elsarticle-template-harv.tex
Fix highlights

%%Research highlights
\begin{highlights}
\item Energy droughts are defined as periods of low production

\item Three models compared to evaluate renewable energy droughts in Ireland

\item Analysis of 45 years of ERA5 weather data for energy drought trends

\item Diverse energy mix reduces drought frequency and duration significantly

\item Model choice impacts energy drought results
\end{highlights}

>>>>

%%Research highlights
\begin{highlights}
\item The C3S-Energy dataset provides renewable energy capacity factor time series

\item Two C3S-Energy and one custom models are compared to assess RES droughts in Ireland

\item RES drought trends are explored by analysing 45 years of ERA5 weather data

\item Diverse energy mix reduces RES drought frequency, duration and extremes

\item Model selection is crucial in the accurate identification of RES droughts

\end{highlights}
